CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot

### 2023-05-03 paper.tex
Update paper
A little bit of stuff on Why3; create diagram

\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{libertinus}

@@

\title{CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot}
\author{Taylor Allred (taylor.allred21@gmail.com)\\ Ashton Wiersdorf (academics@wiersdorfmail.net)}
\date{Spring 2023}

@@

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\usepackage{hyperref}
\usepackage{fullpage}

@@

\title{CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot}
\author{Taylor Allred \texttt{taylor.allred21@gmail.com}\\ Ashton Wiersdorf \texttt{research@wiersdorfmail.net}}
\date{Spring 2023}

@@

\tableofcontents

@@

Why3 describes itself as ``a platform for deductive program verification''\footnote{https://why3.lri.fr/}---instead of an interactive theorem prover like Coq or the like, Why3 is a layer above.
Why3 provides a language---called WhyML---that can be translated into languages a multitude of theorem provers can understand.
This is neat because we every prover has its strengths---Coq will be a better fit for certain proofs than fully-automated provers, whereas some provers will work without the laborious intervention that Coq requires.
Why3 allows us to have it all.

\subsubsection{Writing specifications}

% How do we know that specifications are specific enough? Making tests is one way to check.

\subsubsection{Writing a program}

\subsubsection{Showing the program is faithful to the specification}
